Lifauo Amicus Brief Models

### 2022-05-16 modeling/justicemq-interactions/forgauf.Rmd
add sgfem3 to interaction models

```{r}
mod3 <- glmer(justicevot ~
                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
                forgauf_abortion_regret + forgauf_abortion_regret:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod4 <- glmer(justicevot ~
                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
                forgauf_bad_law + forgauf_bad_law:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod9 <- glmer(justicevot ~
                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
                forgauf_evidence + forgauf_evidence:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod11 <- glmer(justicevot ~
                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
                forgauf_fetus + forgauf_fetus:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod12 <- glmer(justicevot ~
                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
                forgauf_final_authority + forgauf_final_authority:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod14 <- glmer(justicevot ~
                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
                forgauf_morality_religion + forgauf_morality_religion:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod18 <- glmer(justicevot ~
               (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
                forgauf_privacy + forgauf_privacy:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod20 <- glmer(justicevot ~
                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
                forgauf_standing + forgauf_standing:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod23 <- glmer(justicevot ~
                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
                forgauf_undue_burden + forgauf_undue_burden:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod25 <- glmer(justicevot ~
                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
                forgauf_womens_future_life + forgauf_womens_future_life:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod26 <- glmer(justicevot ~
                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
                forgauf_womens_health + forgauf_womens_health:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

>>>>

```{r}
mod3 <- glmer(justicevot ~
                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + sgfem3 + pfemam + 
                forgauf_abortion_regret + forgauf_abortion_regret:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod4 <- glmer(justicevot ~
                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + sgfem3 + pfemam + 
                forgauf_bad_law + forgauf_bad_law:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod9 <- glmer(justicevot ~
                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + sgfem3 + pfemam + 
                forgauf_evidence + forgauf_evidence:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod11 <- glmer(justicevot ~
                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + sgfem3 + pfemam + 
                forgauf_fetus + forgauf_fetus:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod12 <- glmer(justicevot ~
                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + sgfem3 + pfemam + 
                forgauf_final_authority + forgauf_final_authority:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod14 <- glmer(justicevot ~
                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + sgfem3 + pfemam + 
                forgauf_morality_religion + forgauf_morality_religion:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod18 <- glmer(justicevot ~
               (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + sgfem3 + pfemam + 
                forgauf_privacy + forgauf_privacy:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod20 <- glmer(justicevot ~
                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + sgfem3 + pfemam + 
                forgauf_standing + forgauf_standing:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod23 <- glmer(justicevot ~
                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + sgfem3 + pfemam + 
                forgauf_undue_burden + forgauf_undue_burden:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod25 <- glmer(justicevot ~
                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + sgfem3 + pfemam + 
                forgauf_womens_future_life + forgauf_womens_future_life:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod26 <- glmer(justicevot ~
                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + sgfem3 + pfemam + 
                forgauf_womens_health + forgauf_womens_health:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

### 2022-05-16 modeling/justicemq-interactions/legauf.Rmd
add sgfem3 to interaction models

```{r}
mod3 <- glmer(justicevot ~
                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
                legauf_abortion_regret + legauf_abortion_regret:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod4 <- glmer(justicevot ~
                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
                legauf_bad_law + legauf_bad_law:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod9 <- glmer(justicevot ~
                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
                legauf_evidence + legauf_evidence:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod11 <- glmer(justicevot ~
                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
                legauf_fetus + legauf_fetus:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod12 <- glmer(justicevot ~
                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
                legauf_final_authority + legauf_final_authority:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod14 <- glmer(justicevot ~
                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
                legauf_morality_religion + legauf_morality_religion:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod18 <- glmer(justicevot ~
               (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
                legauf_privacy + legauf_privacy:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod20 <- glmer(justicevot ~
                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
                legauf_standing + legauf_standing:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod23 <- glmer(justicevot ~
                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
                legauf_undue_burden + legauf_undue_burden:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod25 <- glmer(justicevot ~
                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
                legauf_womens_future_life + legauf_womens_future_life:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod26 <- glmer(justicevot ~
                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
                legauf_womens_health + legauf_womens_health:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

>>>>

```{r}
mod3 <- glmer(justicevot ~
                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + sgfem3 + pfemam + 
                legauf_abortion_regret + legauf_abortion_regret:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod4 <- glmer(justicevot ~
                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + sgfem3 + pfemam + 
                legauf_bad_law + legauf_bad_law:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod9 <- glmer(justicevot ~
                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + sgfem3 + pfemam + 
                legauf_evidence + legauf_evidence:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod11 <- glmer(justicevot ~
                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + sgfem3 + pfemam + 
                legauf_fetus + legauf_fetus:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod12 <- glmer(justicevot ~
                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + sgfem3 + pfemam + 
                legauf_final_authority + legauf_final_authority:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod14 <- glmer(justicevot ~
                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + sgfem3 + pfemam + 
                legauf_morality_religion + legauf_morality_religion:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod18 <- glmer(justicevot ~
               (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + sgfem3 + pfemam + 
                legauf_privacy + legauf_privacy:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod20 <- glmer(justicevot ~
                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + sgfem3 + pfemam + 
                legauf_standing + legauf_standing:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod23 <- glmer(justicevot ~
                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + sgfem3 + pfemam + 
                legauf_undue_burden + legauf_undue_burden:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod25 <- glmer(justicevot ~
                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + sgfem3 + pfemam + 
                legauf_womens_future_life + legauf_womens_future_life:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod26 <- glmer(justicevot ~
                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + sgfem3 + pfemam + 
                legauf_womens_health + legauf_womens_health:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

### 2022-05-16 modeling/justicemq-interactions/legauo.Rmd
add sgfem3 to interaction models

```{r}
mod3 <- glmer(justicevot ~
                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + poppam + 
                legauo_abortion_regret + legauo_abortion_regret:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod4 <- glmer(justicevot ~
                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + poppam + 
                legauo_bad_law + legauo_bad_law:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod9 <- glmer(justicevot ~
                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + poppam + 
                legauo_evidence + legauo_evidence:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod11 <- glmer(justicevot ~
                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + poppam + 
                legauo_fetus + legauo_fetus:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod12 <- glmer(justicevot ~
                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + poppam + 
                legauo_final_authority + legauo_final_authority:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod14 <- glmer(justicevot ~
                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + poppam + 
                legauo_morality_religion + legauo_morality_religion:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod18 <- glmer(justicevot ~
               (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + poppam + 
                legauo_privacy + legauo_privacy:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod20 <- glmer(justicevot ~
                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + poppam + 
                legauo_standing + legauo_standing:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod23 <- glmer(justicevot ~
                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + poppam + 
                legauo_undue_burden + legauo_undue_burden:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod25 <- glmer(justicevot ~
                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + poppam + 
                legauo_womens_future_life + legauo_womens_future_life:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod26 <- glmer(justicevot ~
                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + poppam + 
                legauo_womens_health + legauo_womens_health:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

>>>>

```{r}
mod3 <- glmer(justicevot ~
                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + sgfem3 + poppam + 
                legauo_abortion_regret + legauo_abortion_regret:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod4 <- glmer(justicevot ~
                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + sgfem3 + poppam + 
                legauo_bad_law + legauo_bad_law:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod9 <- glmer(justicevot ~
                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + sgfem3 + poppam + 
                legauo_evidence + legauo_evidence:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod11 <- glmer(justicevot ~
                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + sgfem3 + poppam + 
                legauo_fetus + legauo_fetus:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod12 <- glmer(justicevot ~
                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + sgfem3 + poppam + 
                legauo_final_authority + legauo_final_authority:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod14 <- glmer(justicevot ~
                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + sgfem3 + poppam + 
                legauo_morality_religion + legauo_morality_religion:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod18 <- glmer(justicevot ~
               (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + sgfem3 + poppam + 
                legauo_privacy + legauo_privacy:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod20 <- glmer(justicevot ~
                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + sgfem3 + poppam + 
                legauo_standing + legauo_standing:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod23 <- glmer(justicevot ~
                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + sgfem3 + poppam + 
                legauo_undue_burden + legauo_undue_burden:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod25 <- glmer(justicevot ~
                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + sgfem3 + poppam + 
                legauo_womens_future_life + legauo_womens_future_life:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod26 <- glmer(justicevot ~
                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + sgfem3 + poppam + 
                legauo_womens_health + legauo_womens_health:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

### 2022-05-16 modeling/justicemq-interactions/lifauo.Rmd
add sgfem3 to interaction models

```{r}
mod3 <- glmer(justicevot ~
                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + poppam + 
                lifauo_abortion_regret + lifauo_abortion_regret:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod4 <- glmer(justicevot ~
                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + poppam + 
                lifauo_bad_law + lifauo_bad_law:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod9 <- glmer(justicevot ~
                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + poppam + 
                lifauo_evidence + lifauo_evidence:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod11 <- glmer(justicevot ~
                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + poppam + 
                lifauo_fetus + lifauo_fetus:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod12 <- glmer(justicevot ~
                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + poppam + 
                lifauo_final_authority + lifauo_final_authority:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod14 <- glmer(justicevot ~
                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + poppam + 
                lifauo_morality_religion + lifauo_morality_religion:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod18 <- glmer(justicevot ~
               (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + poppam + 
                lifauo_privacy + lifauo_privacy:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod20 <- glmer(justicevot ~
                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + poppam + 
                lifauo_standing + lifauo_standing:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod23 <- glmer(justicevot ~
                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + poppam + 
                lifauo_undue_burden + lifauo_undue_burden:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod25 <- glmer(justicevot ~
                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + poppam + 
                lifauo_womens_future_life + lifauo_womens_future_life:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod26 <- glmer(justicevot ~
                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + poppam + 
                lifauo_womens_health + lifauo_womens_health:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

>>>>

```{r}
mod3 <- glmer(justicevot ~
                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + sgfem3 + poppam + 
                lifauo_abortion_regret + lifauo_abortion_regret:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod4 <- glmer(justicevot ~
                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + sgfem3 + poppam + 
                lifauo_bad_law + lifauo_bad_law:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod9 <- glmer(justicevot ~
                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + sgfem3 + poppam + 
                lifauo_evidence + lifauo_evidence:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod11 <- glmer(justicevot ~
                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + sgfem3 + poppam + 
                lifauo_fetus + lifauo_fetus:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod12 <- glmer(justicevot ~
                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + sgfem3 + poppam + 
                lifauo_final_authority + lifauo_final_authority:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod14 <- glmer(justicevot ~
                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + sgfem3 + poppam + 
                lifauo_morality_religion + lifauo_morality_religion:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod18 <- glmer(justicevot ~
               (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + sgfem3 + poppam + 
                lifauo_privacy + lifauo_privacy:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod20 <- glmer(justicevot ~
                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + sgfem3 + poppam + 
                lifauo_standing + lifauo_standing:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod23 <- glmer(justicevot ~
                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + sgfem3 + poppam + 
                lifauo_undue_burden + lifauo_undue_burden:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod25 <- glmer(justicevot ~
                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + sgfem3 + poppam + 
                lifauo_womens_future_life + lifauo_womens_future_life:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod26 <- glmer(justicevot ~
                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + sgfem3 + poppam + 
                lifauo_womens_health + lifauo_womens_health:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))
